A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-31 faculty.tex
updates

\subsection{Journals}
In some fields, journals are more common and prestigious. Moreover, many areas have top journals in additions to well-known conferences (e.g., in addition to the main fource confs as mentioned above, SE also has Trans. of Software Engr. or TSE, which is a very well-known and high-quality journal).  Typically, or at least in SE, the common approach is publishing new work to conference and followup work to journals (e.g., so the journal paper is an substantial extension of the conf. paper with new experiments, studies, theorems, etc). In some sense, journals are for more mature work, and conferences are for new ideas.

@@

However, this does not mean you should not work with your adviser(s). You can absolutely continue do research and write grant proposals with them, but you should also work and write papers with other people, and especially your students.

@@

\chapter{Obtaining Funding}\label{chap}
Without a doubt, grants are one of the most, if not \emph{the} most, important factors in P\&T (or any kind of performance) evaluation.  The most common reason for not getting tenure is the lack of funding. Ideally research results, e.g., publications (\autoref{chap:research}), would be the more important thing for a researcher; but in reality, funding is often considered more important for P\&T at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity. More practically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

@@

\section{From a P\&T Point of View}

@@

At the end of each semester, students are asked to evaluate the instructor. The results are shared anonymously with the instructor to help them improve their teaching and course. Teaching evaluation is also commonly used in annual and tenure evaluation.

@@

Successfully mentoring students is a key and most rewarding part of your job as a faculty member. 
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.  
For P\&T you will be expected to have successes in mentoring students.  For most good universities, eou will likely need to graduate at least one PhD student to get tenure.

@@

Officially services are counted for only 10\% of your work. However, they are very important for your tenure and career.
%You are expected to have certain types of services as a faculty member.  
Some services are required (e.g., when your department chair assigns you to some committees), but some are not and can be declined (e.g., an invitation to be a PC member).

@@

\paragraph{Personal Experience} I mostly cold email people for opportunities. For example, I directly email OOPSLA and PLDI PC chairs and asked, and they invited. I tried this with ICSE (and also nominate myself through the official form), and it never works, even though I have many papers at ICSE (that leaves a bad taste in my mouth about ICSE, but that is another story).  I also got invited to serve on a PC because a senior colleague recommended me.
For NSF, I just emailed program managers and asked to serve on their panels, and they invited me.

@@

I will skip the details and just summarize several things that I didn't like.

>>>>

\subsection{Journals}
In some fields, journals are more common and prestigious. Moreover, many areas have top journals in additions to well-known conferences (e.g., in addition to the main four confs as mentioned above, SE also has Trans. of Software Engr. or TSE, which is a very well-known and high-quality journal).  Typically, or at least in SE, the common approach is publishing new work to conference and followup work to journals (e.g., so the journal paper is an substantial extension of the conf. paper with new experiments, studies, theorems, etc). In some sense, journals are for more mature work, and conferences are for new ideas.

@@

However, this does not mean you should not work with your adviser(s). You can continue doing research and write grant proposals with them, but you should also work and write papers with other people, and especially your students.

@@

\chapter{Funding and Grant Proposals}\label{chap}
Without a doubt, grants are one of the most, if not \emph{the} most, important factors in P\&T (or any kind of performance) evaluation.  The most common reason for not getting tenure is the lack of funding. Ideally research results, e.g., publications (\autoref{chap:research}), would be the more important thing for a researcher; but in reality, funding is often considered more important for P\&T at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity. More practically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

@@

@@

At the end of each semester, students are asked to evaluate the instructor. The results are shared anonymously with the instructor to help them improve their teaching. Teaching evaluation is also commonly used in annual and tenure evaluation.

@@

Successfully mentoring students is a key and most rewarding part of your job as a faculty member. 
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.  
For P\&T you will need to successfully mentoring students.  Many universities expect you to need to graduate at least one PhD student to get tenure.

@@

Officially services are counted for only 10\% of your work. However, they are very important for your P\&T and career in general.
%You are expected to have certain types of services as a faculty member.  
Some services are required (e.g., when your department chair assigns you to some committees), but some are not and can be declined (e.g., an invitation to be a PC member).

@@

\paragraph{Personal Experience} I mostly cold email people for opportunities. For example, I directly email OOPSLA and PLDI PC chairs and asked, and they invited me. I tried this with ICSE (and also nominate myself through the official form), and it never works, even though I have many papers at ICSE. 
For NSF, I just emailed program managers and asked to serve on their panels, and they invited me.

@@

I will skip the details and just summarize several important and disappointing events.
